---
title: "Catal DB Code Exploration"
author: "cengel @ stanford"
date: 'Last updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_notebook:
    highlight: tango
    theme: readable
    code_folding: hide    
---

```{r setup, include=FALSE}
# root dir depends on local setup
myDir <- '/Users/cengel/Anthro/Catal/CodeAnalysis/'
knitr::opts_knit$set(root.dir=normalizePath(myDir))

# read file
code_all <- read.csv("CodeAll.csv")

# libraries
library(ggplot2)
```

### How many lines of code, including everything?
```{r}
nrow(code_all)
```

### How many scripts?
```{r}
length(unique(code_all$filename))
```

### 10 longest scripts
**Do we need to review some of the scripts if they are really used, like `xxxtestunitshe` (?)**

```{r}
# need to group by team. some scripts have same names but are in different teams
# could also use the csv field: `tail(sort(table(code_all$csv)), 10)`
tt <- aggregate(code ~ team + filename, data = code_all, FUN = length)
ttt <- tt[order(tt$code, decreasing = T),]
head(ttt, n=10)
```


### Distribution of length (lines) per script
```{r}
ggplot(code_all, aes(x = reorder(csv, csv, function(x) - length(x)))) +
  geom_bar() + 
  theme(axis.ticks.x = element_blank(), 
        axis.text.x = element_blank()) +
  xlab("")
```

### How many teams
```{r}
length(unique(code_all$team))
```

### How many scripts per team?
```{r}
uu <- unique(code_all[c("team", "filename")])
as.data.frame(table(uu$team))
```


### How many lines of code per team?
```{r}
as.data.frame(all_per_team <- table(code_all$team))

ggplot(code_all, aes(x = reorder(team, team, function(x) + length(x)))) +
  geom_bar() + 
  xlab("") +
  coord_flip()
```

### Comment line/code line ratio per team
```{r}
code_per_team <- with (code_all[code_all$c_marker == 0,], table(team)) # lines with executable code only
(comment_code_ratio <- as.data.frame((all_per_team - code_per_team)/code_per_team))
ggplot(comment_code_ratio) + geom_bar(aes(x=reorder(Var1, Freq), y=Freq), stat = "identity") + 
  geom_hline(yintercept = sum(code_all$c_marker > 0)/nrow(code_all), color="red", linetype="dotted") +
  xlab("") + ylab("comment code ratio and mean") + coord_flip()
```


### More things to do:
- remove automatically generated scripts and do the same as above.
- how to identify reuse of code
    - scripts that are used in several teams
- how to identify age of code chunks
- how to bring together (potentially changing) team reserach agenda with code?

